---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(tidyquant)
library(timetk)
library(dplyr)
library(ggplot2)
acciones = c("TSLA","AAPL","AMZN","NFLX","GOOG")
weights = c(0.25,0.25,0.20,0.15,0.15)
datos<- acciones %>% tq_get(get = "stock.prices")
```

# Investment-Portfolio Analysis
### Stock selection

The complete code for this project is available at `Investment-Portafolio-Analysis.R`


First we will take a series of stocks with which we are going to analyze. These actions were a personal choice but the analysis can be performed with any set of actions. Future projects will explore methods for choosing a portfolio of financial assets. 
The shares selected with their corresponding percentages are in the portfolio the following:

STOCKS        | WEIGHT 
------------- | ------------- 
TSLA          | 25% 
AAPL          | 25% 
AMZN          | 20%
NFLX          | 15%
GOOG          | 15%

Let's take a look at the dataset to see what format it will take.

```{r, echo = FALSE}
head(datos)
```
***
### Statistics and portfolio return

A series of calculations and analyses were made on the data in order to obtain the cumulative return of the portfolio.

```{r pressure, echo = FALSE}
Retorno_Individual <- datos %>%
  group_by(symbol) %>%
  tq_transmute( mutate_fun = periodReturn,
               select = adjusted, period = "daily", col_rename = "Ret")
agrupacion <- tibble(symbol = acciones, wts = weights)
ret_data <- left_join(Retorno_Individual , agrupacion, by = 'symbol')
ret_porc <- ret_data %>% mutate(retornopp = wts * Ret)
port_ret <- ret_porc %>% group_by(date) %>% summarise(port_ret = sum(retornopp))
port_cumulative_ret <- port_ret %>% mutate(cr= cumprod(1 + port_ret))
port_cumulative_ret %>%
  ggplot(aes(x = date, y = cr)) +
  geom_line() +
  labs(x = 'Date',
       y = 'Cumulative Returns',
       title = 'Portfolio Cumulative Returns') +
  theme_classic() +
  scale_y_continuous(breaks = seq(1,2,0.1)) +
  scale_x_date(date_breaks = 'year',
               date_labels = '%Y')
print("The portfolio return is %")
Por_anual <- port_cumulative_ret %>% 
  tq_performance(Ra = port_ret,
                 performance_fun = Return.annualized)
cat("The average annual portfolio returns is ", round((Por_anual[[1]] * 100),2),"%", sep = "")
vola_d <- sd(port_cumulative_ret$port_ret)                    
cat("The daily portfolio volatility is", round((vola_d),4))
vola_a <- vola_d *sqrt(252)
```


It can be seen that the portfolio has a very good performance. With an average annual return that is much higher than financial instruments with high security such as government bonds or debt instruments. In addition, the volatility of the portfolio is quite low, so the risk is clearly reduced. One calculation that is quite valuable is the Sharpe Ratio, which can give us a better idea of the performance of the portfolio. 



```{r, echo = FALSE}
SR <- Por_anual$AnnualizedReturn / vola_a
SRA <- port_cumulative_ret %>% tq_performance(Ra = port_ret, performance_fun = SharpeRatio.annualized) %>% .[[1]]
cat("The annual portfolio sharpe ratio calculated using the tq_performance function is", round((SRA),4))
```

***

### Portfolio optimization

Now that the most important statistics about the portfolio are known, we will look for the best combination on the percentage corresponding to each stock. For this, a series of simulations were made in which different combinations are made and the sharpe ratio is measured to know which of them is the ideal one.
